|

### 2015-12-09 manuscript/manuscript_wtc3.Rmd
small edits
authors commented out

this version used in thesis draft1

\
Courtney E. Campany^1^, Belinda Medlyn^1^, Mark Tjoelker^1^, Susanne von Caemmerer^2^, Remko A. Duursma^1^.

\
^1^ Hawkesbury Institute for the Environment, Western Sydney University, Locked Bag 1797, Penrith, NSW, Australia

\
^2^ Plant Science Division, Research School of Biology, The Australian National University, Canberra, ACT, Australia

@@

##read table ready dataframes
resourcetab <- read.csv("master_scripts/resource_table.csv", stringsAsFactors = FALSE)
getab <- read.csv("master_scripts/ge_table.csv", stringsAsFactors = FALSE)
pval <- c(0.785, 0.001, 0.028, 0.002, 0.001, 0.3486, 0.6385, 0.973)
pval2 <- c(0.001,	0.001,	0.001,	0.001,	0.001,	0.005,	0.001,	0.001)
# getab <- read.csv("master_scripts/ge_table.csv")

@@

\
If shade leaves "lie in wait" for sunflecks then perhaps we should consider an alternate leaf economic strategy to maximize C gain, beyond conventional trade-offs associated with canopy resource distribution. This is because the role of g~s~ in regulating photosynthetic induction impacts the capacity of a leaf to utilize sunflecks [@way2012sunflecks]. If the valuation of sunflecks as a C resource is large enough then costs of sub-optimal stomatal behaviour could be offset over the leaf lifespan. For example, the potential C gain in leaves where sunflecks constitute a large proportion of total daily PFFD may be large enough to tolerate decreases in ITE However, accounting for the heterogeneous nature of light within a canopy remains a current challenge for empirical and modelling studies. Thus, models which predict leaf photosynthesis from N distribution within a canopy will be incomplete unless inclusion of canopy light extinction and the integration of sunflecks on shade leaves are included [@de1997simple].

@@

```{r airvars, fig.width=7, fig.height=9, echo=FALSE,warning=FALSE,dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/air_vars.R")
```
\
**Figure 3.S1**. Daily maximum and minimum temperature (a) and total daily PPFD (b) for each chamber across the experiment duration.
\
```{r acc, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE,dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/ACc_figure.R")
```  
\
**Figure 3.S2**. Photosynthetic CO~2~ response (AC~c~) curves for sun and shade leaves at elevated and ambient temperature treatments. C~c~ values were predicted with g~m~, thus curves represent chloroplastic photosynthetic parameters at 25°C and saturating light (1800 $\mu$mols m^-1^ s^-1^).  
\
```{r gasex_temp3, fig.width=7, fig.height=10, echo=FALSE,warning=FALSE,dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/gasex_temp3.R")
```  
\
**Figure 3.S3**. Response of A (a), g~m~ (b) and C~i~-C~c~ to leaf temperature for sun leaves and shade leaves at low and high light. Shaded symbols represents each monthly measurement campaign. Solid lines, colored by leaf and light type, are fitted line for the relationship with each parameter and leaf temperature across all measurement campaigns. All parameters with no relationship are fitted with zero slope and the overall mean value for each treatment combination. Weak negative relationships with g~m~ and increasing leaf temperature were detected with sun and shade leaves under their local light environment (R^2^ = 0.16 and 0.08, respectively). 
\
```{r gasex_temp4, fig.width=7, fig.height=10, echo=FALSE,warning=FALSE,dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/gasex_temp4.R")
```  
\
**Figure 3.S4**. Response of VPD (a), g~s~ (b) and C~a~-C~i~ to leaf temperature for sun leaves and shade leaves at low and high light. Shaded symbols represents each monthly measurement campaign. Solid lines, colored by leaf and light type, are fitted line for the relationship with each parameter and leaf temperature across all measurement campaigns. All parameters with no relationship are fitted with zero slope and the overall mean value for each treatment combination. Leaf VPD inside the gas exchange cuvette was positively correlated with increasing leaf temperature for sun leaves and shade leaves at low and high light (R^2^ = 0.73, 0.58 and 0.72, respectively).

>>>>

<!-- \ -->
<!-- Courtney E. Campany^1^, Belinda Medlyn^1^, Mark Tjoelker^1^, Susanne von Caemmerer^2^, Remko A. Duursma^1^. -->

<!-- \ -->
<!-- ^1^ Hawkesbury Institute for the Environment, Western Sydney University, Locked Bag 1797, Penrith, NSW, Australia -->

<!-- \ -->
<!-- ^2^ Plant Science Division, Research School of Biology, The Australian National University, Canberra, ACT, Australia -->

@@

##read table ready dataframes
resourcetab <- read.csv("master_scripts/resource_table.csv", stringsAsFactors = FALSE)
getab <- read.csv("master_scripts/ge_table.csv", stringsAsFactors = FALSE)
pval <- c(0.781, 0.001, 0.028, 0.002, 0.973, 0.3486, 0.6385, 0.001)
pval2 <- c(0.001,	0.001,	0.001,	0.001,	0.001,	0.005,	0.001,	0.001)
# getab <- read.csv("master_scripts/ge_table.csv")

@@

\
If shade leaves "lie in wait" for sunflecks then perhaps we should consider an alternate leaf economic strategy to maximize C gain, beyond conventional trade-offs associated with canopy resource distribution. This is because the role of g~s~ in regulating photosynthetic induction impacts the capacity of a leaf to utilize sunflecks [@way2012sunflecks]. If the valuation of sunflecks as a C resource is large enough then costs of sub-optimal stomatal behaviour could be offset over the leaf lifespan. For example, the potential C gain in leaves where sunflecks constitute a large proportion of total daily PFFD may be large enough to tolerate decreases in ITE. However, accounting for the heterogeneous nature of light within a canopy remains a current challenge for empirical and modelling studies. Thus, models which predict leaf photosynthesis from N distribution within a canopy will be incomplete unless inclusion of canopy light extinction and the integration of sunflecks on shade leaves are included [@de1997simple].

@@

```{r airvars, fig.width=7, fig.height=8.8, echo=FALSE,warning=FALSE,dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/air_vars.R")
```
\
**Figure 3.S1**. Daily maximum and minimum temperature (a) and total daily PPFD (b) for each chamber across the experiment duration.
\
```{r acc, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE,dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/ACc_figure.R")
```  
\
**Figure 3.S2**. Photosynthetic CO~2~ response (AC~c~) curves for sun and shade leaves at elevated and ambient temperature treatments. C~c~ values were predicted with g~m~, thus curves represent chloroplastic photosynthetic parameters at 25°C and saturating light (1800 $\mu$mols m^-1^ s^-1^).  
\
```{r gasex_temp3, fig.width=7, fig.height=10, echo=FALSE,warning=FALSE,dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/gasex_temp3.R")
```  
\
**Figure 3.S3**. Response of A (a), g~m~ (b) and C~i~-C~c~ to leaf temperature for sun leaves and shade leaves at low and high light. Shaded symbols represents each monthly measurement campaign. Solid lines, colored by leaf and light type, are fitted line for the relationship with each parameter and leaf temperature across all measurement campaigns. All parameters with no relationship are fitted with zero slope and the overall mean value for each treatment combination. Weak negative relationships with g~m~ and increasing leaf temperature were detected with sun and shade leaves under their local light environment (R^2^ = 0.16 and 0.08, respectively). 
\
```{r gasex_temp4, fig.width=7, fig.height=10, echo=FALSE,warning=FALSE,dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/gasex_temp4.R")
```  
\
**Figure 3.S4**. Response of VPD (a), g~s~ (b) and C~a~-C~i~ to leaf temperature for sun leaves and shade leaves at low and high light. Shaded symbols represents each monthly measurement campaign. Solid lines, colored by leaf and light type, are fitted line for the relationship with each parameter and leaf temperature across all measurement campaigns. All parameters with no relationship are fitted with zero slope and the overall mean value for each treatment combination. Leaf VPD inside the gas exchange cuvette was positively correlated with increasing leaf temperature for sun leaves and shade leaves at low and high light (R^2^ = 0.73, 0.58 and 0.72, respectively).
